Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-02-08 src-latex/main-paper.tex
Update ack

\bigskip
\noindent\textbf{Acknowledgments}\\
{
\footnotesize
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.
%
The authors want to thank S. Bacciochi and P. Cristofoli for helping to create the reference dataset, 
L. Morice for annotating data,
as well as G. Thomas, P. Abi Saad, R. Lelièvre, D. Mignon, T. Cavaciuti and P. Sadki for contributing to the annotation platform.
}
%
% Full names
% Stéphane Bacciochi
% Pascal Cristofoli
% Laureencia Morice
% Guillaume Thomas
% Paul Abi Saad
% Raphaël Lelièvre
% Dorian Mignon
% Thibault Cavaciuti
% Pierre Sadki

>>>>

\bigskip
\noindent\textbf{Acknowledgments}\\
{
\footnotesize
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.
%
The authors want to thank S.~Bacciochi, P.~Cristofoli and J.~Perret for helping to create the reference dataset, 
L.~Morice for annotating data,
as well as G.~Thomas, P.~Abi Saad, R.~Lelièvre, D.~Mignon, T.~Cavaciuti and P.~Sadki for contributing to the annotation platform.
}
%
% Full names
% Stéphane Bacciochi
% Pascal Cristofoli
% Laureencia Morice
% Guillaume Thomas
% Paul Abi Saad
% Raphaël Lelièvre
% Dorian Mignon
% Thibault Cavaciuti
% Pierre Sadki
